hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-06-25 inst/manuscript/paper.Rmd
Box 4 clarification

Next, we generated a simulated thermal regime featuring an ascending thermograph with a mean temperature of 16 °C and standard deviation 1 °C (available in `paper.Rmd`, chosen to represent a reasonable putative temperature regime). Using this dataset, we apply the custom models for each species using `predict_phenology()` (only Smallmouth Bass shown below):

>>>>

Next, to emulate a wild environment, we simulated a thermal regime featuring an ascending thermograph with a mean temperature of 16 °C and standard deviation 1 °C (available in `paper.Rmd`, chosen to represent a reasonable putative temperature regime). To highlight how different species develop at different rates under identical thermal conditions, we apply the custom models for each species using `predict_phenology()` (only Smallmouth Bass shown below):
